Report on Late Winter2013 Production: Image Differencing

### 2013-03-21 W13report.tex
Added Wcs figs.
By eye inspection of false detections.

The numbers of false detections in each best case are given in
Table~\ref{tab-bestfp10}.  For the best cases, there are {\it no}
false detections that associate with an input source to within 2'',
indicating that the residuals are all likely fluctuations in the
backgrounds.  We also list the ratio of negatively detected to
positively detected DiaSources.  That this ratio is significantly
greater than 1.0 in most cases suggests that there is an
oversubtraction of the background in the process, which biases this
ratio (see Section~\ref{sec-bg}).  The optimal configuartions yielding
these false detection rates are given in Table~\ref{tab-bestconfig10}.

@@

@@

\begin{table}
\centering
\begin{tabular}{clccc}
\hline
\multicolumn{5}{|c|}{Best Results: Production 10} \\
\hline
Visit    & Prefilter & False Detections: Matches & False Detections: Orphans & Nneg / Npos \\
\hline
v6866601 & True      & 0                         & 70  & 1.8 \\
         & False     & 0                         & 143 & 2.9 \\
v6866602 & True      & 0                         & 42  & 2.2 \\
         & False     & 0                         & 53  & 0.7 \\
v6866603 & True      & 0                         & 23  & 2.8 \\
         & False     & 0                         & 36  & 3.0 \\
\end{tabular}
\caption{Total number of {\tt DiaSources} detected at 5--sigma from
  all 9 sensors in raft 2,2, for the configurations that yielded the
  lowest number of false positives.  Matches are determined using a
  2'' match radius with the input reference catalog.  Objects with the
  {\tt EDGE} flag are ignored.  The final column lists ratios of the
  number of negatively detected false detections to those with
  positive flux. \label{tab-bestfp10}}
\end{table}

@@

>>>>

The numbers of false detections in each best case are given in
Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
difference images to associate the DiaSources with Sources in the
images.  These by--eye associations are listed in the Matches column
of Table~\ref{tab-bestfp10}, while the remainder are listed in the
Orphans column.  A significant number of the Matches (e.g. both the
matches for v6866603) are actually DiaSources on the very edge of the
image, but which do not have the EDGE bit set.

indicating that the residuals are all likely fluctuations in the
backgrounds.

We also list the ratio of negatively detected to
positively detected DiaSources.  That this ratio is significantly
greater than 1.0 in most cases suggests that there is an
oversubtraction of the background in the process, which biases this
ratio (see Section~\ref{sec-bg}).  The optimal configuartions yielding
these false detection rates are given in Table~\ref{tab-bestconfig10}.

@@

The variance in the prefilterd and postfiltered images is likely to be
different due to the different types of operations that have happened
on the images.  We quantify this by taking the postfiltered images,
immediately before the detection step (i.e. $D'$), and compare the
variance plane to that coming from the prefiltered image.  For
v6866601, which is a deconvolution in the postfiltered production, we
find that the variance is 70\% higher when postfiltering.  This is
consistent with the expectation that deconvolution increases the noise
properties of the image.

For v6866602 and v6866603, we find that the variance is 3--4\% and
2--3\% higher in the {\it prefiltered} data, respectively.  The
primary culprit for this is that the prefiltered data will have gone
through 1 less convolution, meaning less of the variance will have
been lost to covariance.  In this case, the variance plane will be
closer to the truth than in the postfiltered data, but still not
exact.  Assuming that most of the covariance happens during
Psf--matching and Psf--filtering (the astrometric warping kernel is
designed to preserve the nosie properties of the image, although this
is not an exact conservation in practice), the variance plane of the
prefiltered data should itself be $\sim$3\% lower than the emperical
variance in the image plane.  {\it TEST ME}.

@@

\begin{table}
\centering
\begin{tabular}{clccc}
\hline
\multicolumn{5}{|c|}{Best Results: Production 10} \\
\hline
Visit    & Prefilter & False Detections: Matches & False Detections: Orphans & Nneg / Npos \\
\hline
v6866601 & True      & 59                        & 70  & 1.8 \\ 
         & False     & 99                        & 44  & 2.9 \\
v6866602 & True      & 7                         & 35  & 2.2 \\
         & False     & 8                         & 45  & 0.7 \\
v6866603 & True      & 1                         & 22  & 2.8 \\
         & False     & 1                         & 35  & 3.0 \\
%v6866601 & True      & 11                        & 70  & 1.8 \\ SUBTRACT ME!
%         & False     & 99                        & 143 & 2.9 \\
%v6866602 & True      & 7                         & 42  & 2.2 \\
%         & False     & 8                         & 53  & 0.7 \\
%v6866603 & True      & 1                         & 23  & 2.8 \\
%         & False     & 1                         & 36  & 3.0 \\
\end{tabular}
\caption{Total number of {\tt DiaSources} detected at 5--sigma from
  all 9 sensors in raft 2,2, for the configurations that yielded the
  lowest number of false positives.  Matches are determined using a
  2'' match radius with the input reference catalog.  Objects with the
  {\tt EDGE} flag are ignored.  The final column lists ratios of the
  number of negatively detected false detections to those with
  positive flux. \label{tab-bestfp10}}
\end{table}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/wcs_shift.eps} \\
\caption{Wcs shift.}
\label{wcsshift}
\end{figure}

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/wcs_rms.eps} \\
\caption{Wcs rms.}
\label{wcsrms}
\end{figure}
